Irt plot extra

### 2022-08-29 manuscript_v1.Rmd
Version 2--to address the comments

```{r corplot, include =F}
#This chunk holds code for plotting the correlation matrix

p.mat <- correlation::cor_to_p(correlations$rho, 428, method = "polychoric")

corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.2,
                      # insig = "blank",
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,  colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 35),
         axis.text.y = element_text(size = 35),
          legend.text=element_text(size =30),
         legend.title = element_blank(),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
        # legend.position = 'right', 
        # legend.spacing.x = unit(0.5, 'cm'),
        # legend.text = element_text(margin = margin(t = 10)))
#to show pvalue in the fig add p.mat=p.mat
# ggsave("Figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 600, bg ="white")

@@

```{r efa-plot, include=F}
#This chunk holds code for compiled factor identification plots

>>>>

```{r corplot, include =F}
#This chunk holds code for plotting the correlation matrix
#
p.mat <- correlation::cor_to_p(correlations$rho, 428, method = "polychoric")

corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.2,
                      # insig = "blank",
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,  colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 90),
         axis.text.y = element_text(size = 90),
         legend.text=element_text(size =90),
         legend.title = element_text(size =90),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
        # legend.position = 'right', 
        # legend.spacing.x = unit(0.5, 'cm'),
        # legend.text = element_text(margin = margin(t = 10)))
#to show pvalue in the fig add p.mat=p.mat
# ggsave("Figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 300, bg ="white")

@@

```{r efa-plot, eval=FALSE, include=FALSE}
#Not in use. Figure developed using illustrator.
#This chunk holds code for compiled factor identification plots
